\subsubsection{Use case tables}

\begin{usecase}

\addtitle{Use case name}{Create a repeating event } 

\addfield{Participating Actors:}{Initiated by Client \newline Communicates with Server}

\addscenario{Flow of events:}{
	\item The CLIENT creates a new event
	\item The CLIENT Fills out event form
	\item The CLIENT Clicks repeat
	\item The CLIENT Selects interval
	\item The CLIENT Saves Event. \newline - SERVER Synchronizes calendar
}

\additemizedfield{Entry \mbox{conditions:}}{
	\item Calendar must exist in the CLIENT?s user profile
}

\additemizedfield{Exit \mbox{conditions:}}{
	\item Event must have been saved by the CLIENT
	\item Calendar must be synchronized with the SERVER
}

\caption{Use case tabel 1 \label{overflow}}
\end{usecase}

\pagebreak

\begin{usecase}

\addtitle{Use case name}{Share an existing event with another user} 

\addfield{Participating Actors:}{Initiated by Client \newline Communicates with Server and Other_User}

\addscenario{Flow of events:}{
	\item The CLIENT chooses an event.
	\item The CLIENT clicks Edit Event button
	\item The CLIENT clicks on the SHARE button.
	\item The CLIENT enters the username or email of another user he would like to share his event with.
	\item The CLIENT clicks the SEND button.
	\newline - The SERVER sends an invitation to the OTHER_USER.
	\newline - The SERVER sends a notification ?Event shared? to the CLIENT.
	\item The CLIENT reads the notification from the SERVER.
	\item The CLIENT closes the notification.
}

\additemizedfield{Entry \mbox{conditions:}}{ % mbox to force the word no to break over several lines
	\item The CLIENT must have an existing event.
	\item The CLIENT must be connected to the internet.
	\item The CLIENT must know the email or username of the recipient. 

}

\additemizedfield{Exit \mbox{conditions:}}{
	\item The OTHER_USER must have received the invitation. 
}
\caption{Use case tabel 2 \label{overflow}}
\end{usecase}

\pagebreak

\begin{usecase}

\addtitle{Use case name}{Set two reminders on an existing event} 

\addfield{Participating Actors:}{Initiated by Client \newline Communicates with Server}

\addscenario{Flow of events:}{
	\item The CLIENT chooses an event
	\item The CLIENT clicks Edit Event button
	\item The CLIENT clicks Set Reminder
	\item The CLIENT selects two reminders
	\item The CLIENT sets the time when the reminder should notify the client
	\item The CLIENT chooses Reminder Type ?Email? for reminder 1 and   Reminder Type ?Notification? for reminder 2
	\item The CLIENT saves the event
	\item The SERVER sends an email to the CLIENT when the first reminder is fired
	\item The SERVER notifies the CLIENT when the second reminder is fired

}

\additemizedfield{Entry \mbox{conditions:}}{
	\item The CLIENT must have a calendar with a future existing event
	\item The CLIENT must have a live connection to the internet

}

\additemizedfield{Exit \mbox{conditions:}}{
	\item The CLIENT must be able to add reminders to an event
}
\caption{Use case tabel 3 \label{overflow}}
\end{usecase}