\section{Functional Requirements}

\subsection*{Calender}
The Calendar is used to keep track of events, e.g. Work calendar or Holiday calendar. The Calendar contains events specific to only itself.
A new calendar is initiated by the Client with a name that described the calendar. The Calendar can be modified by the Client.
 A Calendar may contain one or more events. The system can contain multiple calendars.

\subsection*{Event}
An Event has a start date and an end date.
An Event belongs to a Calendar. Events are initiated by the Client and can also be modified by the Client.
An Event may repeat on multiple dates, e.g. every week/month.
Events have alarms that be set to notify the user

\subsection*{Client}
The Client manages both the Calendars and the Events.
The Client has access to all of his Calendars and Events and can therefore create, edit, share and delete Calendars and Events.
The Client can change the view.
The Client has the ability to Hide/Show different Calendars of their liking.
The Client can synchronize the Calendars with the Server to they are easily accessible on different devices.
The Client has the opportunity to search for specific events.

\subsection*{Server}
The Server is responsible for keeping the Client?s calendars up to date.
When an Event or Calendar is shared the Server must send an invitation to the recipient(s).

\subsection*{Other user}
The Other User receives invitations from the Client and can choose to either accept or decline the invitation.

\subsection*{View}
The are four types of view: Day View, Week View, Month View, Year View.
Besides the view can show one or more Calendars at the same time.